One-armed spirals in locally isothermal, radially structured self-gravitating discs

### 2015-01-13 paper/paper.tex
almost done with first revision

{\bf We employ direct hydrodynamic simulations using three different
  grid-based codes to demonstrate how this `background torque' 
  can lead to the growth of one-armed spirals in radially structured, 
  self-gravitating discs. This is despite the fact that our disc
  models do not meet the requirements for the `SLING' 
  mechanism. Although our numerical simulations consider
  self-gravitating discs, the `background torque' is generic for
  locally isothermal discs and its existence does not require
  disc self-gravity. Thus, the destabilisation effect we
  describe should also be applicable to non-self-gravitating discs.  
}

>>>>

{\bf We employ direct hydrodynamic simulations using three different
  grid-based codes to demonstrate how this `background torque' 
  can lead to the growth of one-armed spirals in radially structured, 
  self-gravitating discs. This is despite the fact that our disc
  models do not meet the requirements for the `SLING' 
  mechanism. Although our numerical simulations consider
  self-gravitating discs, this `background torque' is generic for
  locally isothermal discs and its existence does not require
  disc self-gravity. Thus, the destabilisation effect we
  describe should also be applicable to non-self-gravitating discs.  
}
